### 2013-01-03 exercise2/paper.tex
added some lines in paper

\paragraph{}This is a template.

\section{Data set section}

>>>>

\paragraph{}This assignment is about extending a Bayes Network Classifier by adding a custom search algorithm.

\section{Setup}

Used stuff: R. RWeka -- an interface in R for Weka. implement a searcher by extending a java class from the weka library/framework. running a R script that starts the weka BayesNet-classifier with our custom searcher.
